### 2015-12-13 ada-ftrl-proofs.tex
Fix README, capitalize titles in bibfile, etc.

\begin{proof}[Proof of Lemma~\ref{lemma:recurrence-solution}]
We prove the lemma by induction on $T$.  The base case $T=0$ is trivial. For $T
\ge 1$, we have
$$
\Delta_T
\le \Delta_{T-1} + \min \left\{a_T, \ \frac{a_T^2}{\Delta_{T-1}} \right\}
\le \sqrt{3 \sum_{t=1}^{T-1} a_t^2} + \min \left\{ a_T, \frac{a_T^2}{\sqrt{3 \sum_{t=1}^{T-1} a_t^2}} \right\}
$$
where the first inequality follows from Lemma~\ref{lemma:gap-recurrence}, and
the second inequality from the induction hypothesis and the fact that the
function $f(x) = x + \min\{a_T, a_T^2/x\}$ is increasing on $[0,\infty)$.  It
remains to prove that
$$
\sqrt{3 \sum_{t=1}^{T-1} a_t^2} + \min \left\{ a_T, \frac{a_T^2}{\sqrt{3 \sum_{t=1}^{T-1} a_t^2}} \right\}
\le  \sqrt{3 \sum_{t=1}^T a_t^2} \; .
$$
If $a_T = 0$, the inequality clearly holds. Dividing through by $a_T$ and
making substitution $z=\frac{\sqrt{\sum_{t=1}^{T-1} a_t^2}}{a_T}$, leads to
$$
z\sqrt{3} + \min\left\{1,\frac{1}{z\sqrt{3}}\right\} \le \sqrt{3 + 3z^2}
$$
which can be easily checked by considering separately the cases $z \in
[0,\frac{1}{\sqrt{3}})$ and $z \in [\frac{1}{\sqrt{3}}, \infty)$.
\end{proof}

>>>>

\begin{proof}[Proof of Lemma~\ref{lemma:recurrence-solution}]
We prove the lemma by induction on $T$.  The base case $T=0$ is trivial. For $T
\ge 1$, we have
$$
\Delta_T
\le \Delta_{T-1} + \min \left\{a_T, \ \frac{a_T^2}{\Delta_{T-1}} \right\}
\le \sqrt{3 \sum_{t=1}^{T-1} a_t^2} + \min \left\{ a_T, \frac{a_T^2}{\sqrt{3 \sum_{t=1}^{T-1} a_t^2}} \right\}
$$
where the first inequality follows from Lemma~\ref{lemma:gap-recurrence}, and
the second inequality from the induction hypothesis and the fact that the
function $f(x) = x + \min\{a_T, a_T^2/x\}$ is increasing on $[0,\infty)$.  It
remains to prove that
$$
\sqrt{3 \sum_{t=1}^{T-1} a_t^2} + \min \left\{ a_T, \frac{a_T^2}{\sqrt{3 \sum_{t=1}^{T-1} a_t^2}} \right\}
\le  \sqrt{3 \sum_{t=1}^T a_t^2} \; .
$$
If $a_T = 0$, the inequality clearly holds. Otherwise, $a_T$ is positive and we
divide through by it and make substitution $z=\frac{\sqrt{\sum_{t=1}^{T-1}
a_t^2}}{a_T}$, which leads to
$$
z\sqrt{3} + \min\left\{1,\frac{1}{z\sqrt{3}}\right\} \le \sqrt{3 + 3z^2}
$$
which can be easily checked by considering separately the cases $z \in
[0,\frac{1}{\sqrt{3}})$ and $z \in [\frac{1}{\sqrt{3}}, \infty)$.
\end{proof}
